### 2020-08-26 README.Rmd
adapt to mlr3 "extra_args" approach during Task construction

| Literature                           | Package    | Reference     | mlr3 Sugar                     |
|--------------------------------------|------------|---------------|--------------------------------|
| Spatial Buffering                    | blockCV    | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking                     | blockCV    | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                           | sperrorest | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking               | blockCV    | Valavi 2019   | `rsmp("spcv-env")`             |
| \-                                   | \-         | \-            | `rsmp("sptcv-cluto")`          |
| Leave-Location-and-Time-Out          | CAST       | Meyer 2018    | `rsmp("sptcv-cstf")`           |
| ---                                  | ---        | ---           | ---                            |
| Repeated Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking                | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
| \-                                   | \-         | \-            | `rsmp("repeated-sptcv-cluto")` |
| Repeated Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("repeated-sptcv-cstf")`  |

>>>>

| Literature                  | Package    | Reference     | mlr3 Sugar                     |
|-----------------------------|------------|---------------|--------------------------------|
| Spatial Buffering           | blockCV    | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking      | blockCV    | Valavi 2019   | `rsmp("spcv-env")`             |
| \-                          | \-         | \-            | `rsmp("sptcv-cluto")`          |
| Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("sptcv-cstf")`           |
| ---                         | ---        | ---           | ---                            |
| Repeated Spatial Blocking   | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV         | sperrorest | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking       | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
| \-                          | \-         | \-            | `rsmp("repeated-sptcv-cluto")` |
